Reproducible Research: Peer Assessment 1
========================================

## Loading and preprocessing the data

```{r}
unzip("activity.zip")
data <- read.csv("activity.csv", header = TRUE)
```

## What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day.

```{r}
steps_per_day <- aggregate(steps ~ date, data, sum)
hist(steps_per_day, main = "Histogram of Total Number of Steps Taken Each Day", xlab = "Steps Taken Each Day")
```

2. Calculate and report the **mean** and **median** total number of steps taken per day.

```{r}
mean(steps_per_day$steps)
median(steps_per_day$steps)
```

## What is the average daily activity pattern?

1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis).

```{r}
steps_interval <- aggregate(steps ~ interval, data, mean)
plot(steps_interval$steps, type="l", main = "Average Number of Steps Per 5-min Interval", 
    xlab = "Interval", ylab = "Number of Steps")
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
max_steps_interval = which.max(steps_interval$steps)
```

## Imputing missing values

1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
sum(is.na(activity))
```

2. Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

I will use the mean for the 5-minute intervals as fillers for missing values.

3. Create a new dataset that is equal to the original dataset but with the missing data filled in.



## Are there differences in activity patterns between weekdays and weekends?
