Reproducible Research: Peer Assessment 1
========================================

## Loading and preprocessing the data

```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day.

```{r}
steps_per_day <- aggregate(steps ~ date, activity, sum)
hist(steps_per_day)
```

2. Calculate and report the **mean** and **median** total number of steps taken per day.

```{r}
mean(steps_per_day$steps)
median(steps_per_day$steps)
```

## What is the average daily activity pattern?

1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis).

```{r}
steps_interval <- aggregate(steps ~ interval, activity, mean)
plot(steps_interval$steps, type="l")
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
max_steps_interval = which.max(steps_interval$steps)
```

## Imputing missing values

1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
sum(is.na(activity))
```

Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.


## Are there differences in activity patterns between weekdays and weekends?
